Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-03-19 Masterarbeit_Robotik_Pamuk.tex
Added zotero and clean.sh
Added progress bar

The methodology of this thesis consists of several steps. First, a comprehensive literature review is conducted to understand the current trends and challenges in real-time robot control. Based on the literature study, a suitable virtualisation platform is selected. After the selection of the virtualisation platform, the robot control platform is implemented. This step includes the installation and configuration of Salamander OS, Xenomai, QEMU and PCV-521 in the Yocto environment. Once the platform has been implemented, the robot is connected via a VARAN bus interface. Finally, the platform is evaluated to determine how the integration of real-time functions and efficient communication systems improves the response time and reliability of robot applications.

@@

\clearpage 
\chapter{Hauptteil}
\clearpage
\chapter{Resultate}
\clearpage
\chapter{Diskussion}
\clearpage
\chapter{Zusammenfassung und Ausblick}

>>>>

In diesem Abschnitt werden sämtliche theoretischen Konzepte und Randbedingungen sowie praktische Methoden, die zur Erreichung der Zielsetzung dieser Masterarbeit beigetragen haben, detailliert beschrieben.

Diese Masterarbeit wurde in Zusammenarbeit mit der Firma SIGMATEK erstellt.

First, a comprehensive literature review is conducted to understand the current trends and challenges in real-time robot control. Based on the literature study, a suitable virtualisation platform is selected. After the selection of the virtualisation platform, the robot control platform is implemented. This step includes the installation and configuration of Salamander OS, Xenomai, QEMU and PCV-521 in the Yocto environment. Once the platform has been implemented, the robot is connected via a VARAN bus interface. Finally, the platform is evaluated to determine how the integration of real-time functions and efficient communication systems improves the response time and reliability of robot applications.

@@

\clearpage 
\chapter{Hauptteil}
\clearpage
\chapter{Results}
\clearpage
\chapter{Discussion}
\clearpage
\chapter{Summary and Outlook}
I am using \cite{blackadarHistoricalReviewCauses2016} for citing.
